State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-05-24 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex

		\State Backward iteration: for $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $ calculate the sigma points $\mathcal X_{i,t}^b$ and propogate them through equation \ref{eq:QmatrixForSigmapoints}

@@

			\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b,u_t) 

>>>>

		\State Backward iteration: for $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $ calculate the sigma points $\mathcal X_{i,t}^b$ and propagate them through equation \ref{eq:QmatrixForSigmapoints}

@@

			\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b) 
